---
title: "Thread Analisys"
author: "J.P.G."
date: "Summer 2018"
Developers:
  Guillem G.:
  Pol S.:
Writer:
  Jeffrey M.:
---

```{r}
library(DataDrivenSecFirehol)
```


Threat intel based on firehol's IP lists
=============================

## About this repo

This package will be an extra tool to any one searching data from an IP that was part of an intrusion, a DoS or other kind of attaks ...

The program is initiated with `DataDrivenSecFirehol()`.
Functions which control DDSFirehol's behavior include `bye()` to quit and `help()` to prompt a help menu.

The data source we extract information from was:
[firehol](https://github.com/firehol/firehol)

## Hands-On 

First of all lets download the data and unzip them. The process might take a while so hold on.
```{r}
path.raw.data <- DataDrivenSecFirehol::downloadFireHolData()
path.raw.data <- paste(path.raw.data, "blocklist-ipsets-master", sep="\\")
path.raw.data <- paste(path.raw.data, "\\", sep="")
```
The data will be in `r path.raw.data`. It's a temporary file that will be deleted once you finish the session.

Let's proceed with the parsing and creation of a sorted data-frame.

```{r}
df <- DataDrivenSecFirehol::tidyDataIPs(raw.path = path.raw.data)
```


Since all the IPs has been parsed, let's do the same for the geolocation of the IPs; for that we will use maxmind
Frist of all remove the IPs of the continents in order to don't duplicate data and keep just the required information.

```{r}
df2 <- DataDrivenSecFirehol::tidyDataCountries(raw.path = path.raw.data)
```

Once both frames are builded and ready, let's merge them since a bigger dataframe will be able to handle all the data.

```{r}
df_final <- DataDrivenSecFirehol::mergeDFs2(df,df2)
```

## Using the functions 
Use `help()`to see the available functions
## License

This program is free software; you can redistribute it and/or modify it under the terms of the GNU General Public License as published by the Free Software Foundation; either version 2 of the License, or (at your option) any later version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License for more details.